Manual of comparing optimal subsampling with model robust optimal subsampling method for logistic regression (exponential distribution)

### 2022-06-24 Manual.Rmd
updated manual with Full diagram for spelling mistakes

---
title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for LogisticRegression (Exponential Distribution)"
output: github_document
---

@@

* Use **Articles.Rmd** to generate plots relevant to the paper as pdf files **SMSE_MI_LR_TV_Nor_mMSE.pdf** and **SMSE_MI_LR_TV_Nor_mVc.pdf**.

>>>>

---
title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for logistic regression (exponential distribution)"
output: github_document
---

@@

* Use **Articles.Rmd** to generate plots relevant to the paper as pdf files **SMSE_MI_LR_TV_Exp_mMSE.pdf** and **SMSE_MI_LR_TV_Exp_mVc.pdf**.
